Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
minor edit

We can thus get an approximated visualisation of our object as soon as we run
the application, allowing for real time interactions with the object (changing
the visualized value, curvature radius, \ldots). It is also clear on those
graphs that using a hierarchical decomposition reduces the curvature computation
time. For the XYZ-Dragon with $R=20$, it needs almost 4 seconds to compute the
$l_0$ level, whereas using the hierarchical algorithm, it only needs 700ms.
However, due to the precomputation, this algorithm is biased and creates an
error (presented in Table~\ref{tab:full-res-stat}) that needs to be considered.

>>>>

We can thus get an approximated visualisation of our object as soon as we run
the application, allowing for real time interactions with the object (changing
the visualized value, curvature radius, \ldots). It is also clear on those
graphs that using a hierarchical decomposition reduces the curvature computation
time, especially with big radii. For the XYZ-Dragon with $R=20$, it needs almost
4 seconds to compute the $l_0$ level, whereas using the hierarchical algorithm,
it only needs 700ms. However, due to the precomputation and current hierarchical
structure, this algorithm is biased and creates an error (presented in
Table~\ref{tab:full-res-stat}) that needs to be considered.
